---
title: "R Notebook"
output: html_notebook
---
```{r}
## install.packages("tidytuesdayR")
library(tidytuesdayR)
tuesdata <- tidytuesdayR::tt_load('2025-02-11')

cdc_datasets <- tuesdata$cdc_datasets
fpi_codes <- tuesdata$fpi_codes
omb_codes <- tuesdata$omb_codes

write.csv(cdc_datasets, "~/Desktop/github/DatasetPractice/cdc_datasets.csv", row.names = FALSE)
write.csv(fpi_codes, "~/Desktop/github/DatasetPractice/fpi_codes.csv", row.names = FALSE)
write.csv(omb_codes, "~/Desktop/github/DatasetPractice/omb_codes.csv", row.names = FALSE)

```

General Data Exploration Questions

    1.Can you describe the structure of the datasets you are working with?
    2.What are the key features (columns) in each dataset, and how do they relate to each other?
    3.Are there any missing values in these datasets? How would you handle them?
    4.How would you identify and remove duplicate records in these datasets?
    5.What types of data do these datasets contain (categorical, numerical, text, etc.)?
    
```{r}
#1.Can you describe the structure of the datasets you are working with?
head(cdc_datasets)
head(fpi_codes)
head(omb_codes)

```

